### 2019-05-03 README.Rmd
contributing_guidelines
gosset_belongs_to_agrobioinfoservices

@@

    library("devtools")
    devtools::install_github("kauedesousa/gosset", upgrade = "never")

@@

>>>>

[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/agrobioinfoservices/gosset?branch=master&svg=true)](https://ci.appveyor.com/project/kauedesousa/gosset)

Package website: https://agrobioinfoservices.github.io/gosset/

@@

    library("devtools")
    devtools::install_github("agrobioinfoservices/gosset", upgrade = "never")

@@

## Going further

The full functionality of **gosset** is illustrated in the package vignette. The vignette can be found on the [package website](https://agrobioinfoservices.github.io/gosset/) or from within R once the package has been installed.

## Contribution

You are welcome to contribute to this project. Please read our [contribution guide lines](CONTRIBUTING.md).
